---
title: "Running forcing through time by Scenario"
author: "Ezekiel Adekoya"
date: "2025-02-05"
output: html_document
---

Set up directories
```{r setup, include=TRUE}
library("here")
dir <- setwd(here())
knitr::opts_knit$set(root.dir = "~/Mac/Dropbox/Desktop/Eastern-Scotian-Shelf-Model/")
knitr::opts_knit$set(root.dir = dir)

# Define the save directory
save_dir <- paste0(here(), "/Ess_Output/")
```

Function to randomize interaction matrix while preserving basic ecological constraints
```{r}
# Function to randomize interaction matrix while preserving basic ecological constraints
randomize_interaction_matrix <- function(params, sdev = 0.1) {
  # Get current interaction matrix
  old_inter <- params@interaction
  # Get current interactions for seal predation 
  old_seal <- gear_params(params)$catchability[14:26]
  
  # Create noise matrix with same dimensions
  n <- nrow(old_inter)
  noise <- matrix(rnorm(n*n, mean = 0, sd = sdev), nrow = n)
  noise_seal <- rnorm(n, mean = 0, sd = sdev)
  
  # Add noise while preserving symmetry
  new_inter <- old_inter * exp(noise)
  new_seal <-  old_seal*exp(noise_seal)
    
  # Ensure diagonal remains 0.5
  #diag(new_inter) <- 0.5
  
  # Ensure values stay between 0 and 1
  new_inter[new_inter > 1] <- 1
  new_inter[new_inter < 0] <- 0
  new_seal[new_seal > 1] <- 1
  new_seal[new_seal < 0] <- 0
  
  
  # Update parameters
  params@interaction <- new_inter
  gear_params(params)$catchability[14:26]<-new_seal 
  
  return(params)
}

```

Function to run multiple simulations with different interaction matrices
```{r}
# Function to run multiple simulations with different interaction matrices
run_random_sims <- function(params, n_sims = 10, years = 100, sd = 0.1,effort_scen) {
  # List to store simulation results
  sim_results <- list()
  
  # Run simulations
  for(i in 1:n_sims) {
    # Create new parameters with randomized interaction matrix
    rand_params <- randomize_interaction_matrix(params, sd = sd)
    # Run to steady
    rand_params<-steady(rand_params)
    # Run simulation
    sim <- project(rand_params, effort=effort_scen)
    
    # Store results
    sim_results[[i]] <- sim
  }
  
  return(sim_results)
}

```

Set up packages:
```{r}
# Set up packages:
# Load required library
library(mizer)
library(mizerExperimental)
library(Metrics)
library(tidyverse)
library(interp)
library(hydroGOF)
library(patchwork)
library(ggpubr)
```

Read in params object
```{r}
# Read in params object
# Read in params object
params_with_seal <- readRDS("Ess_data/params_with_seal_interaction.RDS")
# Read in effort object
effort_with_seal <- readRDS("Ess_data/effort_with_seal_matrix.RDS")
effort<-effort_with_seal
# set up zero effort for sim without seals
effort[,"Seals"]<-0
#fix zero effort values for American Plaice
effort["2004","AMERICAN PLAICE"]<-sum(effort[c("2003","2005"),"AMERICAN PLAICE"])/2
#params = params_with_seal
#Orignal run
sim0 <- project(params,effort = effort)
plotlyBiomass(sim0)

# Run single simulation with randomized matrix as a test
rand_params <- randomize_interaction_matrix(params)
sim1 <- project(rand_params,effort = effort)
plot(sim1,time_range=c(1970:1980))
plotBiomassRelative(sim1,sim0)

# use sam eparams object but set Seal "effort" to 0 for without additonal mort runs
effort<-effort_with_seal
effort[,"Seals"] <- 0
# Run multiple simulations
sims_scen1 <- run_random_sims(params_with_seal, n_sims = 1000,effort_scen=effort,sd=0.2)
sims_scen2 <- run_random_sims(params_with_seal, n_sims = 1000,effort_scen=effort_with_seal,sd=0.2)

# Save sim outputs
#saveRDS(sims_scen1,"Ess_output/sims_scen1.RDS")
 #saveRDS(sims_scen2,"Ess_output/sims_scen2.RDS")

sims_scen1<-readRDS("Ess_output/sims_scen1.RDS")
sims_scen2<-readRDS("Ess_output/sims_scen2.RDS")

# Check results from first simulation
plot(sims_scen2[[2]],time_range=c(1970:1980))

plotBiomassRelative(sims_scen2[[99]],sim0)

# read in biomass and catches data
yield_ts<-readRDS("Ess_data/yield_ts.RDS")
yield_ts<-yield_ts |> rename(Yield_Obs=Yield) |> filter(Species!="SANDLANCES")
biomass_ts<-readRDS("Ess_data/biomass_ts.RDS")
biomass_ts<-biomass_ts |> rename(Biomass_Obs=Biomass) 

```

Figures - make plot of obs and sims
```{r}
# Figures - make plot of obs and sims
#BIOMASS
sim_bio<-lapply(sims_scen1,getBiomass,min_w=species_params(params)$biomass_cutoff)
sim_bio2<-lapply(sims_scen2,getBiomass,min_w=species_params(params)$biomass_cutoff)

df_sim_bio<-do.call(rbind.data.frame, sim_bio)
df_sim_bio$sim<-rep(1:1000, each=41)
df_sim_bio$year<-rep(1970:2010,100)

df_sim_bio2<-do.call(rbind.data.frame, sim_bio2)
df_sim_bio2$sim<-rep(1:1000, each=41)
df_sim_bio2$year<-rep(1970:2010,1000)


sim_mean<-df_sim_bio |> pivot_longer(c(1:13)) |> mutate(Year=year,Species=as.factor(name)) |> group_by(Species,Year) |>summarise(Biomass=median(value))|> ungroup()
sim_lower<-df_sim_bio |> pivot_longer(c(1:13))|> mutate(Year=year,Species=as.factor(name))  |> group_by(Species,Year) |>summarise(Biomass=min(value))|> ungroup() 
sim_upper<-df_sim_bio |> pivot_longer(c(1:13))|> mutate(Year=year,Species=as.factor(name))  |> group_by(Species,Year) |>summarise(Biomass=max(value))|> ungroup() 


sim_mean2<-df_sim_bio2 |> pivot_longer(c(1:13)) |> mutate(Year=year,Species=as.factor(name)) |> group_by(Species,Year) |>summarise(Biomass=median(value))|> ungroup()
sim_lower2<-df_sim_bio2 |> pivot_longer(c(1:13)) |> mutate(Year=year,Species=as.factor(name)) |> group_by(Species,Year) |>summarise(Biomass=min(value))|> ungroup()
sim_upper2<-df_sim_bio2 |> pivot_longer(c(1:13)) |> mutate(Year=year,Species=as.factor(name)) |> group_by(Species,Year)|>summarise(Biomass=max(value))|> ungroup()

sim1 <-data.frame(Species=sim_mean$Species, 
                  Year=sim_mean$Year,
                   sim_mean=sim_mean$Biomass,
                   sim_lower=sim_lower$Biomass,
                   sim_upper=sim_upper$Biomass,
                   scen=rep("Scen1", length(sim_mean$Biomass)))

sim1 <-left_join(biomass_ts,sim1)

sim2 <-data.frame(Species=sim_mean2$Species, 
                  Year=sim_mean2$Year,
                  sim_mean=sim_mean2$Biomass,
                  sim_lower=sim_lower2$Biomass,
                  sim_upper=sim_upper2$Biomass,
                  scen=rep("Scen2", length(sim_mean2$Biomass)))

sim2 <-left_join(biomass_ts,sim2)


time_series <- rbind(sim1,sim2)
time_series <- time_series |> rename(Biomass=Biomass_Obs)

time_series <- time_series  %>%
  mutate(scen = ifelse(Year<1986,
                         "Calibration",scen))

species<-levels(time_series$Species)<- c("AMERICAN PLAICE", "ATLANTIC COD","ATLANTIC HALIBUT", "HERRING","REDFISH UNSEPARATED", "GREENLAND HALIBUT", "HADDOCK","SANDLANCES", "SILVER HAKE", "SPINY DOGFISH",  "WHITE HAKE", "WITCH FLOUNDER", "YELLOWTAIL FLOUNDER")

maxw<-species_params(params)$w_max
species<-data.frame(species,maxw)
species<-species[order(species$maxw),"species"]
```

reorder Species in the plot to go from from small to large max body size.
```{r}
# reorder Species in the plot to go from from small to large max body size.
time_series <- time_series |> arrange(Species) |> mutate(Species=factor(Species,species))

time_series <- time_series %>%
  rename(Scenario =  scen )
biomass_plot_with <- ggplot(time_series, aes(x = Year, y = Biomass, colour = Scenario, fill = Scenario)) +
  facet_wrap(~factor(Species, levels = c("SANDLANCES","HERRING", "WITCH FLOUNDER", "REDFISH UNSEPARATED",   "YELLOWTAIL FLOUNDER", "SILVER HAKE", "AMERICAN PLAICE", "GREENLAND HALIBUT", "HADDOCK", "SPINY DOGFISH", "WHITE HAKE",  "ATLANTIC COD", "ATLANTIC HALIBUT")), scales="free") +
  geom_point(aes(y = Biomass), colour = "black", size = 0.5) +
  geom_ribbon(aes(ymin = sim_lower, ymax = sim_upper), alpha = 0.3, colour = NA) +
  geom_line(aes(y = sim_mean)) +
  scale_colour_manual(name = NULL,  # Removes legend title
                      values = c("grey70", "#4575B4", "#D73027"),
                      labels = c("Calibration", "Fishing mortality only", "Fishing with additional mortality")) +
  scale_fill_manual(name = NULL,  # Removes legend title
                    values = c("grey70", "#4575B4", "#D73027"),
                    labels = c("Calibration", "Fishing mortality only", "Fishing with additional mortality")) +
  geom_vline(xintercept = 1986, linetype = "dashed", color = "black") +
  theme_pubr() +
  theme(
    legend.position = "bottom",
    axis.title.x = element_blank()
  )+
  guides(colour = guide_legend(title = NULL), fill = guide_legend(title = NULL))  # Remove legend headings
ggsave(filename = paste0(save_dir, "biomass_plot_with.jpeg"), plot = biomass_plot_with,
       width = 11, height = 8.5, units = "in",dpi = 400)
```

Figure for CATCHES 
```{r}
# Figure for CATCHES 
# remove 'Gear' == Seals from yields

trimYield<-function(sim){
  
  y<-plotYieldGear(sim, return_data = T)
  y<-filter(y,Gear!="Seals")
  y<-select(y,c(Year, Species,Yield))
  return(y)
  
}

#trimYield(sims_scen1[[1]])

sim_catches<-lapply(sims_scen1,trimYield)
sim_catches2<-lapply(sims_scen2,trimYield)
for (i in 1:1000) {
  sim_catches[[i]]$sim<-i
  sim_catches2[[i]]$sim<-i
}

df_sim_catch<-do.call(rbind.data.frame, sim_catches)
df_sim_catch2<-do.call(rbind.data.frame, sim_catches2)

sim_mean_c<-df_sim_catch |>  group_by(Species,Year) |>summarise(Yield=median(Yield))|> ungroup()
sim_lower_c<-df_sim_catch |> group_by(Species,Year) |>summarise(Yield=min(Yield))|> ungroup() 
sim_upper_c<-df_sim_catch |> group_by(Species,Year)|>summarise(Yield=max(Yield))|> ungroup() 


sim_mean2_c<-df_sim_catch2 |> group_by(Species,Year) |> summarise(Yield=median(Yield))|> ungroup()
sim_lower2_c<-df_sim_catch2 |> group_by(Species,Year)|> summarise(Yield=min(Yield))|> ungroup()
sim_upper2_c<-df_sim_catch2 |> group_by(Species,Year)|> summarise(Yield=max(Yield))|> ungroup()

sim1_c <-data.frame(Species=sim_mean_c$Species, 
                  Year=sim_mean_c$Year,
                  sim_mean=sim_mean_c$Yield,
                  sim_lower=sim_lower_c$Yield,
                  sim_upper=sim_upper_c$Yield,
                  scen=rep("Scen1", length(sim_mean_c$Yield)))

sim1_c <-right_join(yield_ts,sim1_c)

sim2_c <-data.frame(Species=sim_mean2_c$Species, 
                  Year=sim_mean2_c$Year,
                  sim_mean=sim_mean2_c$Yield,
                  sim_lower=sim_lower2_c$Yield,
                  sim_upper=sim_upper2_c$Yield,
                  scen=rep("Scen2", length(sim_mean2_c$Yield)))

sim2_c <-right_join(yield_ts,sim2_c)


time_series_c <- rbind(sim1_c,sim2_c)
time_series_c <- time_series_c  %>%
  mutate(scen = ifelse(Year<1986,
                       "Calibration",scen))
time_series_c <- time_series_c |> rename(Yield=Yield_Obs)

```

Reorder Species in the plot to go from from small to large max body size.
```{r}
# Reorder Species in the plot to go from from small to large max body size.
# species_c<-species[-1] #remove sandlances as not fished
time_series_c <- subset(time_series_c,!is.na(time_series_c$Species))
species<-levels(time_series_c $Species)<- c("AMERICAN PLAICE", "ATLANTIC COD","ATLANTIC HALIBUT", "HERRING","REDFISH UNSEPARATED", "GREENLAND HALIBUT", "HADDOCK","SANDLANCES", "SILVER HAKE", "SPINY DOGFISH",  "WHITE HAKE", "WITCH FLOUNDER", "YELLOWTAIL FLOUNDER")
yield_plot_with = ggplot(time_series_c, aes(x=Year, y=Yield, colour=scen, fill=scen)) +
  facet_wrap(~factor(Species, levels = c("HERRING", "WITCH FLOUNDER", "REDFISH UNSEPARATED",   "YELLOWTAIL FLOUNDER", "SILVER HAKE", "AMERICAN PLAICE", "GREENLAND HALIBUT", "HADDOCK", "SPINY DOGFISH", "WHITE HAKE",  "ATLANTIC COD", "ATLANTIC HALIBUT")), scales="free") +
  geom_point(aes(y=Yield), colour="black", size=0.5) +
  geom_ribbon(data = time_series_c, aes(ymin=sim_lower, ymax=sim_upper), alpha=0.3, colour=NA) +
  geom_line(data = time_series_c, aes(y=sim_mean, colour=scen)) +
  scale_colour_manual(name = NULL,  # Removes legend title
                      values = c("grey70", "#4575B4", "#D73027"),
                      labels = c("Calibration", "Fishing mortality only", "Fishing with additional mortality")) +
  scale_fill_manual(name = NULL,  # Removes legend title
                    values = c("grey70", "#4575B4", "#D73027"),
                    labels = c("Calibration", "Fishing mortality only", "Fishing with additional mortality")) +
  labs(y = "Catches") + 
  geom_vline(xintercept = 1986, linetype="dashed", color = "black") +
  theme_pubr() +
  theme(legend.position = "bottom",
        axis.title.x = element_blank())
ggsave(filename = paste0(save_dir, "yield_plot_with.jpeg"), plot = yield_plot_with,
       width = 11, height = 7.5, units = "in",dpi = 400)
yield_plot_with
```


 Comparison of Model Skill Metrics across Model Scenarios
```{r}
# Comparison of Model Skill Metrics across Model Scenarios

# Calculate modStats
library(openair)
time_series_c <- time_series_c |> mutate(logYield = log(Yield),logMeanSimYield=log(sim_mean))
modStats_c <- time_series_c %>%
  group_modify(~modStats(.x, obs = "logYield", mod = "logMeanSimYield", type = "scen", rank = "scen",statistic=c("n","FAC2","MGE","RMSE","r","COE"),method="spearman")) %>%
  ungroup()

time_series <- time_series %>%
  rename(scen =  Scenario)
time_series <- time_series |> mutate(logBiomass = log(Biomass),logMeanSimBiomass=log(sim_mean))
modStats <- time_series %>%
  group_modify(~modStats(.x, obs = "logBiomass", mod = "logMeanSimBiomass", type = "scen", rank = "scen",statistic=c("n","FAC2","MGE","RMSE","r","COE"),method="spearman")) %>%
  ungroup()


## nice table

library(flextable)

tabl_b <-  modStats %>%
  mutate(across(where(is.numeric), ~round(., 3))) %>%
  select(c("scen","n","FAC2","MGE","RMSE","r","COE"))%>%
  flextable()

tabl_c<-modStats_c %>%
  mutate(across(where(is.numeric), ~round(., 3))) %>%
  select(c("scen","n","FAC2","MGE","RMSE","r","COE"))%>%
  flextable()

```

# # Calculate spearman correlation across all simulations
```{r}
# cor_scen2<-cor_scen1<-expand.grid(sim=1:1000,cor_bio=NA,cor_catch=NA)
#  
#  for (i in 1:1000){
# 
#   #scen 1 no additional mortality
#   bio<-plotBiomass(sims_scen1[[i]],return_data = T)
#   yield<-sims_scen1[[i]] |> plotYieldGear(return_data = T)  |> filter(Gear!="Seals") |> filter(Species!="SANDLANCES")
#   yield<- yield_ts %>%
#     left_join(yield,by = c("Year", "Species"))
# 
#   cor_scen1$cor_bio[i]<-cor(bio$Biomass,biomass_ts$Biomass,method="spearman")
#   cor_scen1$cor_catch[i]<-cor(yield$Yield_Obs,yield$Yield,method="spearman",use="pairwise.complete.obs")
#   plot(yield$Yield,yield$Yield_Obs,log="xy")
#   plot(bio$Biomass,biomass_ts$Biomass,log="xy")
# 
#   #scen 2 with additonal mortality
#   bio<-plotBiomass(sims_scen2[[i]],return_data = T)
#   yield<-sims_scen2[[i]] |> plotYieldGear(return_data = T)  |> filter(Gear!="Seals") |> filter(Species!="SANDLANCES")
#   yield<- yield_ts %>%
#     left_join(yield,by = c("Year", "Species"))
# 
#   cor_scen2$cor_bio[i]<-cor(bio$Biomass,biomass_ts$Biomass,method="spearman")
#   cor_scen2$cor_catch[i]<-cor(yield$Yield_Obs,yield$Yield,method="spearman",use="pairwise.complete.obs")
#   plot(yield$Yield,yield$Yield_Obs,log="xy")
#   plot(bio$Biomass,biomass_ts$Biomass,log="xy")
# }
# 
# cor_scen1$scen<-"without additional mortality"
# cor_scen2$scen<-"with additional mortality"
# 
# cor_results<-rbind(cor_scen1,cor_scen2)
# cor_results <- cor_results %>%
#   rename(Biomass = cor_bio, Catch = cor_catch)
# 
# 
# cor_results <- cor_results |> 
#   pivot_longer(cols = c(2, 3), names_to = "Variable") |> 
#   ggplot(aes(x = Variable, y = value, fill = scen)) +
#   geom_violin() + 
#   theme_bw() +  
#   labs(x = NULL, y = "Correlation Value") +  
#   theme(
#     axis.text.x = element_text(angle = 360, hjust = 1, vjust = 1, size = 12, face = "bold"),  # Bold x-axis text
#     axis.text.y = element_text(size = 12, face = "bold"),  # Y-axis labels size 9, bold
#     axis.title.x = element_text(size = 12, face = "bold"),  # X-axis title bold and size 9
#     axis.title.y = element_text(size = 12, face = "bold"),
#    legend.title = element_blank(),
#     legend.text = element_text(size = 10),  # Legend text size
#     legend.position = "right",  # Place legend on the right # Y-axis title bold and size 9
#     panel.grid.major = element_blank()
#   ) +
#   scale_x_discrete(labels = c(expression(bold("Biomass")), expression(bold("Catch"))))  # Bold x-axis categories
# 
# cor_results
# 
# ggsave(filename = paste0(save_dir, "cor_results.jpeg"), plot = cor_results,
#        width = 11, height = 7.5, units = "in",dpi = 400)
```

# compare size-based trophic cascades under each scenario relative to histrorical when cod were abundant
```{r}
spectra_reference<-plotSpectra(sims_scen1[[1]],return_data = T,time_range = 1970:1985)

spectra_scen1<-plotSpectra(sims_scen1[[1]],return_data = T,time_range = 1995:2010)

spectra_scen2<-plotSpectra(sims_scen2[[1]],return_data = T,time_range = 1995:2010)

sf1 <- mutate(left_join(spectra_reference, spectra_scen1, by = c("w", "Legend")), 
             rel_diff =(value.y - value.x)/(value.x + value.y))

sf2 <- mutate(left_join(spectra_reference, spectra_scen2, by = c("w", "Legend")), 
              rel_diff =(value.y - value.x)/(value.x + value.y))

# legend_levels <- intersect(names(sims_scen1[[1]]@params@linecolour), unique(sf$Legend))
# linecolours <- sims_scen1[[1]]@params@linecolour[legend_levels]


# combine
sf1$scenario <- "Fishing mortality alone"
sf2$scenario <- "Fishing with additional mortality"
combined_data <- rbind(sf1, sf2)

linecolours<-c("#4575B4","#D73027")
combined_data <- combined_data %>%
  mutate(Legend = case_when(
    Legend == "TURBOT, GREENLAND HALIBUT" ~ "GREENLAND HALIBUT",
    Legend == "HERRING(ATLANTIC)" ~ "HERRING",
    Legend == "COD(ATLANTIC)" ~ "ATLANTIC COD",
    TRUE ~ Legend  # Leave other values unchanged
  ))
combined_data$Legend <- factor(combined_data$Legend, 
                               levels = c("SANDLANCES", "HERRING", "REDFISH UNSEPARATED", 
                                          "WITCH FLOUNDER", "YELLOWTAIL FLOUNDER", "AMERICAN PLAICE", 
                                          "HADDOCK", "SILVER HAKE", "WHITE HAKE", 
                                          "SPINY DOGFISH", "ATLANTIC COD", 
                                          "ATLANTIC HALIBUT", "GREENLAND HALIBUT", "Resource"))
# Then create the plot
trophic_cascades_plot <- ggplot(combined_data, aes(x = w, y = rel_diff, colour = scenario)) +
  geom_line(linewidth = 0.8) +
  facet_wrap(~Legend, scales = "free") +  # Use 'Legend' for facet_wrap if that’s the intended grouping
  labs(x = "Weight (g)", y = "Symmetric relative difference") +
  scale_x_log10() +
  scale_color_manual(values = linecolours) +
  geom_hline(yintercept = 0, linetype = 1, colour = "dark grey", linewidth = 0.75) +
  theme_bw() +
  theme(
    text = element_text(size = 12, family = "Arial"),
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    legend.title = element_blank(),
    legend.text = element_text(size = 10),
    legend.position = "bottom",
    panel.grid.minor = element_blank(),
    panel.border = element_rect(linewidth = 1),
    panel.grid.major.x = element_blank(), 
    panel.grid.major.y = element_blank() 
  )
ggsave(filename = paste0(save_dir, "trophic_cascades_plot.jpeg"), plot = trophic_cascades_plot,
       width = 11, height = 7.5, units = "in",dpi = 400)
trophic_cascades_plot
```

# Size distribution of seal "diets"
```{r}

aaa =plotYieldVsSize(sims_scen2[[1]],gear=c("Seals"), x_var = c("Length")) + theme_bw()
ggsave(filename = paste0(save_dir, "aaa.jpeg"), plot = aaa,
       width = 11, height = 7.5, units = "in",dpi = 400)
```

# # Calculate spearman correlation across all simulations
```{r}
# Initialize correlation data frames for scenarios 1 and 2
cor_scen1 <- expand.grid(sim = 1:1000, cor_bio = NA, cor_catch = NA, cor_mean = NA)
cor_scen2 <- expand.grid(sim = 1:1000, cor_bio = NA, cor_catch = NA, cor_mean = NA)

# Load the observed data outside the loop
mean_weight_observed <- read.csv("Ess_data/Mean_weight_by_species.csv")

# Load simulation data
sims_scen1 <- readRDS("Ess_output/sims_scen1.RDS")
sims_scen2 <- readRDS("Ess_output/sims_scen2.RDS")


# Check the structure of mean_weight_observed to understand what we're working with
print(str(mean_weight_observed))

# Loop through the simulations
for (i in 1:1000) {
  
  # Scenario 1: No additional mortality
  bio <- plotBiomass(sims_scen1[[i]], return_data = TRUE)
  yield <- sims_scen1[[i]] |> 
    plotYieldGear(return_data = TRUE) |> 
    filter(Gear != "Seals") |> 
    filter(Species != "SANDLANCES")
  yield <- yield_ts %>% left_join(yield, by = c("Year", "Species"))
  
  # Correctly get mean weights for scenario 1
  sim_model <- sims_scen1[[i]]
  sim_mean <- getMeanWeight(sim_model, min_w=species_params(params)$biomass_cutoff, return_data = TRUE)
  
  # Convert named numeric vector to data frame
  Mean_weight_scen1 <- data.frame(
    year = as.numeric(names(sim_mean)),
    MeanWeight = as.numeric(sim_mean)
  )
  
  # Calculate correlations for Scenario 1
  cor_scen1$cor_bio[i] <- cor(bio$Biomass, biomass_ts$Biomass, method = "spearman")
  cor_scen1$cor_catch[i] <- cor(yield$Yield_Obs, yield$Yield, method = "spearman", use = "pairwise.complete.obs")
  
  # Make sure data is properly aligned for mean weight correlation
  # First, check if mean_weight_observed has year column
  if("year" %in% colnames(mean_weight_observed)) {
    # Join datasets by year to ensure proper alignment
    combined_data <- Mean_weight_scen1 %>%
      inner_join(mean_weight_observed, by = "year")
    
    # Now calculate correlation only if there are matching rows
    if(nrow(combined_data) > 0) {
      cor_scen1$cor_mean[i] <- cor(combined_data$MeanWeight, combined_data$Weight, 
                                  method = "spearman", use = "pairwise.complete.obs")
    }
  } else {
    # If no year column, we need to make sure the vectors are the same length
    min_length <- min(nrow(Mean_weight_scen1), nrow(mean_weight_observed))
    cor_scen1$cor_mean[i] <- cor(Mean_weight_scen1$MeanWeight[1:min_length], 
                                mean_weight_observed$Weight[1:min_length], 
                                method = "spearman", use = "pairwise.complete.obs")
  }
  
  # Scenario 2: With additional mortality
  bio <- plotBiomass(sims_scen2[[i]], return_data = TRUE)
  yield <- sims_scen2[[i]] |> 
    plotYieldGear(return_data = TRUE) |> 
    filter(Gear != "Seals") |> 
    filter(Species != "SANDLANCES")
  yield <- yield_ts %>% left_join(yield, by = c("Year", "Species"))
  
  # Correctly get mean weights for scenario 2
  sim_model2 <- sims_scen2[[i]]
  sim_mean2 <- getMeanWeight(sim_model2, min_w=species_params(params)$biomass_cutoff, return_data = TRUE)
  
  # Convert named numeric vector to data frame
  Mean_weight_scen2 <- data.frame(
    year = as.numeric(names(sim_mean2)),
    MeanWeight = as.numeric(sim_mean2)
  )
  
  # Calculate correlations for Scenario 2
  cor_scen2$cor_bio[i] <- cor(bio$Biomass, biomass_ts$Biomass, method = "spearman")
  cor_scen2$cor_catch[i] <- cor(yield$Yield_Obs, yield$Yield, method = "spearman", use = "pairwise.complete.obs")
  
  # Make sure data is properly aligned for mean weight correlation - Scenario 2
  if("year" %in% colnames(mean_weight_observed)) {
    # Join datasets by year to ensure proper alignment
    combined_data <- Mean_weight_scen2 %>%
      inner_join(mean_weight_observed, by = "year")
    
    # Now calculate correlation only if there are matching rows
    if(nrow(combined_data) > 0) {
      cor_scen2$cor_mean[i] <- cor(combined_data$MeanWeight, combined_data$Weight, 
                                  method = "spearman", use = "pairwise.complete.obs")
    }
  } else {
    # If no year column, we need to make sure the vectors are the same length
    min_length <- min(nrow(Mean_weight_scen2), nrow(mean_weight_observed))
    cor_scen2$cor_mean[i] <- cor(Mean_weight_scen2$MeanWeight[1:min_length], 
                                mean_weight_observed$Weight[1:min_length], 
                                method = "spearman", use = "pairwise.complete.obs")
  }
}

# Assign scenario labels
cor_scen1$scen <- "Fishing mortality only"
cor_scen2$scen <- "Fishing with additional mortality"

# Combine results and rename variables
cor_results <- rbind(cor_scen1, cor_scen2)
cor_results <- cor_results %>% 
  rename(Biomass = cor_bio, Catch = cor_catch, Mean_weight = cor_mean)

cor_results_long <- cor_results |> 
  pivot_longer(cols = c("Biomass", "Catch", "Mean_weight"), names_to = "Variable") |>
  # Add this line to rename the variable
  mutate(Variable = ifelse(Variable == "Mean_weight", "Mean body size", Variable))

# Create violin plot
cor_results <- ggplot(cor_results_long, aes(x = Variable, y = value, fill = scen)) + 
  geom_violin() + 
  theme_bw() + 
  labs(x = NULL, y = "Correlation Value") + 
  scale_fill_manual(values = c("blue", "red")) +
  theme(
    axis.text.x = element_text(angle = 0, hjust = 0.5, size = 12, face = "bold"),
    axis.text.y = element_text(size = 11, face = "bold"),
    axis.title.y = element_text(size = 11, face = "bold"),
    legend.title = element_blank(),
    legend.text = element_text(size = 10),
    legend.position = "right",
    panel.grid.major = element_blank()
  )
# Correlation between scenarios
cor_results
cor_results
ggsave(filename = paste0(save_dir, "cor_results.jpeg"), plot = cor_results,
       width = 11, height = 7.5, units = "in",dpi = 400)
```


```{r}

```